Discriminative Sensing Based on Signal Processing for Information Security Analysis

### 2017-11-15 docs/thesis/chapters/4_tensor_dl/tensor_dl.tex
tensor-dl and spell check

Compressed Sensing (CS) aims to obtain the most relevant information of a dataset, what makes it useful for compression, signal reconstruction, image processing and classification, such as in sparce representation classification (SRC) problems.

@@

In the analytic approach, some pre-defined functions are used to construct the dictionary. Curvelets [24], which tracks the shape of the discontinuity set, offers efficient and near-optimal representation of smooth objects. Shearlets [25], which is obtained from dilations, action of translations and shear transformations, has nice geometric properties and mathematical properties for image representation. Bandelets [26], which specifies the geometry as a vector field, is de-signed to improve the image compression and noise reduction performance.

@@

Considering that big data problems require techniques to deal with multidimensional data in order to make sense of strucutre and relationship of many dimensions, and also considering that a key challenge to use sparse coding and dictionary learning for classification is how to find proper dictionaries and coefficients that highligh discriminative structure and relationships of one dataset, this work propose a tensor-based DL for fraud detection from imbalanced data, in order to apply the tensor deconposition for DL methods to evidentiate the discriminative sensing of a fraud detection dataset.

This chapter is organized as follows. Section \ref{sec:4_motivation} presents one experiment and results that motivate the proposed work. In Section \ref{sec:4_relatedworks}, related works are discussed. Section \ref{sec:4_datamodel} presents the data model and the evaluated datasets. Section \ref{sec:4_proposal} describes the proposed approach for for fraud detecton from mobile money transacion. Section \ref{sec:2_experimentalresults} discusses the experimental validation and presents the results, and Section \ref{sec:4_conclusion} draws the conclusions and the suggestions for future work.

@@

\begin{figure}[!htb]
	\centering 
	\includegraphics[width=10cm]{figures/5_20_2000_1000_100.eps}
	\caption{Cumulative atom identificatin per degree rates. $T=2000$, $M=20$, $N=50$}
	\label{fig:fig1}
\end{figure}

Figure \ref{fig:fig2} presents the results for recovering a dictionary of $M=80$ and $N=30$. It is possible to observe that the tensor-base methods outperform MOD, RLS-DLA and K-SVD in number of identified atoms and the required degrees for identification. Note that MOD performs quite silimar to RLS-DLA, while K-SVD is the worst evaluated case for this experiment. Considering the tensor-based methods, T-MOD outperforms K-HOSVD with higher atom identification over lower degrees. The experimental results verify that the tensor-based dictionary learning algorithms are able to identify more dictionary atoms when dealing with larger dictionaries and that they converge faster.

\begin{figure}[!htb]
	\centering 
	\includegraphics[width=10cm]{figures/5_20_2000_24000_100.eps}
	\caption{Cumulative atom identificatin per degree rates. $T=2000$, $M=80$, $N=30$}
	\label{fig:fig2}
\end{figure}

The results reveals that tensor-based algorithms can perform better for dictionary recovery problems when the dictionary size increases. Since dictionary learning and reconstruction error are usually used for sparce representation classification (SRC) problems, it is possible to supose that tensor-based algorithms can improve results of classification problems, as well as can extract hidden patterns and structure in multidimensional data analytics problems.

@@

A key challenge to use SC and DL for classification is how to find proper dictionaries and coefficients that highligh discriminative structure and relationships of one dataset. Therefore, we introduce a tensor-based DL method for fraud detecton from unbalanced data. Specifically, we apply a sparse representation based classification (SRC) method through learning a tensor-based dictionary and evaluate the reconstruction error for fraud classification.

In this chapter, we propose a tensor-based sparse representation and dictionary learning technique to analyze mobile money transactions in order to identify frauds. We propose to use tensor-based DL for learning fraudulent and legitimante data separetelly, and apply the learned dictionaries to reconstruct a test signal and classify it as fraud or ligitimate, according to the minimum reconstruction error measured by some metrics.

@@

Compressed sensing (also known as compressive sensing, compressive sampling, or sparse sampling) is a signal processing technique for efficiently acquiring and reconstructing a signal, by finding solutions to underdetermined linear systems. This is based on the principle that, through optimization, the sparsity of a signal can be exploited to recover it from far fewer samples than required by the Shannon-Nyquist sampling theorem.

@@

One of the key principles of dictionary learning is that the dictionary has to be inferred from the input data. The emergence of sparse dictionary learning methods was stimulated by the fact that in signal processing one typically wants to represent the input data using as few components as possible. Before this approach the general practice was to use predefined dictionaries (such as fourier or wavelet transforms). However, in certain cases a dictionary that is trained to fit the input data can significantly improve the sparsity, which has applications in data decomposition, compression and analysis and has been used in the fields of image denoising and classification, video and audio processing. Sparsity and overcomplete dictionaries have immense applications in image compression, image fusion and inpainting.

MOD \cite{engan1999method} is a DL algorithm that is commonly used for extensions of Least-Squares (LS) type schemes, also known as iterative least squares dictionary learning algorithm (ILS-DLA) \cite{engan2007family}. MOD defines that if we know $\boldsymbol{S}$ in equation \ref{eq:4_eq01}, $\boldsymbol{A}$ can be estimated solving a linear LS problem. Additionally, knowing $\boldsymbol{A}$ we obtain $\boldsymbol{S}$ by solving a sparse recovery problem. MOD iterates between the two steps, starting with an initial guess of $\boldsymbol{A}$, denoted as $\hat{\boldsymbol{A}}$, which can be estimated, generated by previous dictionary learning or generated analitically. Despite - simplicity, the MOD algorithm has been criticized for its slow convergence, which is due to the fact that $\boldsymbol{A}$ and $\boldsymbol{S}$ are updated separately, which may lead to a slow convergence \cite{aharon2006rm}.

@@

Tensor data are typically highly structured, a perfect match for compressive sampling, so that the CS framework relaxes data acquisition requirements, enables compact storage, and facilitates data completion (i.e., inpainting of missing samples due to a faulty sensor or unreliable measurement) \cite{cichocki2015tensor}. Roemer \emph{et al.} \cite{roemer2014tensor} have proposed a tensor-based multidimensional extensions for MOD and K-SVD algorithms, which are respectivelly T-MOD and K-HOSVD, and show their improved performances numerically, for the dictionary reconstruction problem.

Considering that tensor-based algorithms can perform better for dictionary recovery problems when the dictionary size increases, accordint to subsection \ref{sec:4_motivation_results}, we believe that tensor-based DL algorithms can improve the discriminative sensing for classification classification problems. Therefore, we propose use tensor-based DL for learning fraudulent and legitimante data separetelly, and apply the learned dictionaries to reconstruct a test signal and classify it as fraud or ligitimate, according to the minimum reconstruction error measured by some metrics

@@

We adopt a synthetic financial datasets for fraud detection\footnote{https://www.kaggle.com/ntnu-testimon/paysim1} in order to validate our proposal. This dataset is synthetically generated by  PaySim \cite{lopez2016paysim}, which is a financial simulator that simulates mobile money transactions based on an original dataset and provides a synthetic dataset as an approach to such a problem. PaySim uses aggregated data from the private dataset to generate a synthetic dataset that resembles the normal operation of transactions and injects malicious behaviour to later evaluate the performance of fraud detection methods. PaySim simulates mobile money transactions based on a sample of real transactions extracted from one month of financial logs from a mobile money service implemented in an African country. The original logs were provided by a multinational company

The selected dataset is composed by 9 features (variables) and 2.770.408 transactions (observations). It is also provided one lable that classifies each transaction as fraudulent or not. As the majority dataset of anomaly or fraud detection, the data is imbalanced, where the number of fraudulent transactions is 8.213 against 2.762.196 of normal transactions. Therefore, the fraud class represents 0,30 \% of the entire datased.

For evaluation of the proposed classification approach we adopt a data splitting into training and test data, where the training data has 70 \% of the whole dataset. We denote the traning data as $X_r$ and the test data as $X_e$. The dataset can also be divided by normal and fraudulent transactions, where the normal train data is denoted as $X_r^o$, the fraud train data is denoted as $X_r^f$. The same notation of fraud, normal, train and test is applied to qualify $A$ and $S$.

@@

\section{Tensor-based Sparce Representation Classification}
\label{sec:4_proposal}

We propose a Tensor-based Sparce Representation Classification approach to use tensor-based DL for learning fraudulent and legitimante data separetelly, and apply the learned dictionaries to reconstruct a test signal and classify it as fraud or ligitimate, according to the minimum reconstruction error measured by some metrics.

Our proposal requires supervision, where labels of training data are used to classify each transaction as fraud or normal. The first step is to split the training dataset into classes, as fraud or normal, and create respectively the data matrices $\boldsymbol{X}_r^f$ and $\boldsymbol{X}_r^o$. For each data matrix we compute the data normalization and subsequently the initial dictionaries $\boldsymbol{A}_r^f$ and $\boldsymbol{A}_r^o$. Afterward, we apply the dictionaries and the data matrices to the selected DL algorithms, in order to learn the best dictionaries $\boldsymbol{A}_r^f$ and $\boldsymbol{A}_r^o$ that respectivelly represents fraud and normal classes as basis vectors.

With the trainned dictionaries $\boldsymbol{A}_r^f$ and $\boldsymbol{A}_r^o$ and the test data $\boldsymbol{X}_e$ it is possible to process each transacion of $\boldsymbol{X}_e$, denoted as $\boldsymbol{x}_e^t$ where $t$ represents the transaction index, in order to compute its sparse coding from fraud and normal dictionaries, generating respectively $\boldsymbol{S}_e^f$ and $\boldsymbol{S}_e^o$. Subsequently, we compute the signal rescontruction as $\boldsymbol{x}_e^f = \boldsymbol{A}_r^f \cdot \boldsymbol{S}_e^f$ and $\boldsymbol{x}_e^o = \boldsymbol{A}_r^o \cdot \boldsymbol{S}_e^o$.

Finally, we compare $\boldsymbol{x}_e^f$ and $\boldsymbol{x}_e^o$ to $\boldsymbol{x}_e^t$ in order to evaluate the reconstruction error to classify the transaction as fraud or normal according to the minimum reconstruction error from $\boldsymbol{x}_e^f$ and $\boldsymbol{x}_e^o$, respectivelly. We adopt the cosine similarity to compare the reconstructed signal to the original one.

@@

For data analysis of imbalanced classes it is usually applied a data undersample method, where an under sized sample is selected from the original datased, with similar amount of occurrences for each class of the data. This method is efficient for algorithm trainning, but it faces generalization problems when tries to classify new data. Therefore, we propose to evaluate the our proposal for under sampled data and for the complete dataset.

The Receiver Operating Characteristics (ROC) curve makes use of the proportion of two metrics: true positives rate (TPR) and false positives rate (FPR), which are defined as:

@@

ROC curves are commonly used to present results for binary decision problems in machine learning. However, when dealing with highly skewed datasets, Precision-Recall (PR) curves give a more informative picture of an algorithm’s performance \cite{davis2006relationship, he2009learning}. The PR curve is defined by plotting Precision Rate (PR) over the Recall Rate (RR), which are defined as:

\begin{equation}\label{eq:4_eq06}
	PR = \frac{TP}{TP + FP},
\end{equation}

\begin{equation}\label{eq:4_eq07}
	RR = \frac{TP}{TP + FN}.
\end{equation}

PR curves exhibit a strong correspondence to ROC curves: A curve dominates in ROC space if and only if it dominates in PR space. However, an algorithm that optimizes the AUC in the ROC space is not guaranteed to optimize the AUC in PR space. Considering that our data is very imbalanced, with many more negatives than positives values, we adopt the averate precision recall for the classification evaluation

Logistic regression is the most common method used to model binary response data \cite{hilbe2011logistic}, it is useful for situations in where it is necessary to predict the presence or absence of a characteristic, with binary classification, such as in anomaly or fraud detection \cite{bhattacharyya2011data}. Therefore, we compare the results of out proposed approach with the logistic regression algorithm applied for fraud detection from the adopted datase.

@@

% \section{Discussion}
% \label{sec:4_Discussion}

@@

The conclusion goes here.

The importance of the right metric for classification of imbalanced data

Tensor based analysis explores the extructure and relationship of multidimensional data and can improve the discriminative power of imbalanced data for classification

Can be used for feature extraction and used for well known algorithm, and can be used for discriminative classification based on heuristics

Our proposal is better for imbalanced data than others techniques

incorporate discriminative funcions

evaluate other metrics beyond reconstruction, using techniques such as reconstruction with dictionary concatenation

>>>>

Compressed Sensing (CS) aims to obtain the most relevant information of a dataset, what makes it useful for compression, signal reconstruction, image processing and classification, such as in sparse representation classification (SRC) problems.

@@

In the analytic approach, some pre-defined functions are used to construct the dictionary. Curvelets [24], which tracks the shape of the discontinuity set, offers efficient and near-optimal representation of smooth objects. Shearlets [25], which is obtained from dilations, action of translations and shear transformations, has nice geometric properties and mathematical properties for image representation. Bandelets [26], which specifies the geometry as a vector field, is designed to improve the image compression and noise reduction performance.

@@

Considering that big data problems require techniques to deal with multidimensional data in order to make sense of structure and relationship of many dimensions, and also considering that a key challenge to use sparse coding and dictionary learning for classification is how to find proper dictionaries and coefficients that highlight discriminative structure and relationships of one dataset, this work propose a tensor-based DL for fraud detection from imbalanced data, in order to apply the tensor decomposition for DL methods to highlight the discriminative sensing of a fraud detection dataset.

This chapter is organized as follows. Section \ref{sec:4_motivation} presents one experiment and results that motivate the proposed work. In Section \ref{sec:4_relatedworks}, related works are discussed. Section \ref{sec:4_datamodel} presents the data model and the evaluated datasets. Section \ref{sec:4_proposal} describes the proposed approach for fraud detection from mobile money transactions. Section \ref{sec:2_experimentalresults} discusses the experimental validation and presents the results, and Section \ref{sec:4_conclusion} draws the conclusions and the suggestions for future work.

@@

\begin{figure}[!htb]
	\centering 
	\includegraphics[width=10cm]{figures/5_20_2000_1000_100.eps}
	\caption{Cumulative atom identification per degree rates. $T=2000$, $M=20$, $N=50$}
	\label{fig:fig1}
\end{figure}

Figure \ref{fig:fig2} presents the results for recovering a dictionary of $M=80$ and $N=30$. It is possible to observe that the tensor-base methods outperform MOD, RLS-DLA and K-SVD in number of identified atoms and the required degrees for identification. Note that MOD performs quite similar to RLS-DLA, while K-SVD is the worst evaluated case for this experiment. Considering the tensor-based methods, T-MOD outperforms K-HOSVD with higher atom identification over lower degrees. The experimental results verify that the tensor-based dictionary learning algorithms are able to identify more dictionary atoms when dealing with larger dictionaries and that they converge faster.

\begin{figure}[!htb]
	\centering 
	\includegraphics[width=10cm]{figures/5_20_2000_24000_100.eps}
	\caption{Cumulative atom identification per degree rates. $T=2000$, $M=80$, $N=300$}
	\label{fig:fig2}
\end{figure}

The results reveals that tensor-based algorithms can perform better for dictionary recovery problems when the dictionary size increases. Since dictionary learning and reconstruction error are usually used for sparse representation classification (SRC) problems, it is possible to suppose that tensor-based algorithms can improve results of classification problems, as well as can extract hidden patterns and structure in multidimensional data analytics problems.

@@

A key challenge to use SC and DL for classification is how to find proper dictionaries and coefficients that highlight discriminative structure and relationships of one dataset. Therefore, we introduce a tensor-based DL method for fraud detection from unbalanced data. Specifically, we apply a sparse representation based classification (SRC) method through learning a tensor-based dictionary and evaluate the reconstruction error for fraud classification.

In this chapter, we propose a tensor-based sparse representation and dictionary learning technique to analyze mobile money transactions in order to identify frauds. We propose to use tensor-based DL for learning fraudulent and legitimate data separately, and apply the learned dictionaries to reconstruct a test signal and classify it as fraud or legitimate, according to the minimum reconstruction error measured by some metrics.

@@

Compressed sensing (also known as compressive sensing, compressive sampling, or sparse sampling) is a signal processing technique for efficiently acquiring and reconstructing a signal, by finding solutions to undetermined linear systems. This is based on the principle that, through optimization, the sparsity of a signal can be exploited to recover it from far fewer samples than required by the Shannon-Nyquist sampling theorem.

@@

One of the key principles of dictionary learning is that the dictionary has to be inferred from the input data. The emergence of sparse dictionary learning methods was stimulated by the fact that in signal processing one typically wants to represent the input data using as few components as possible. Before this approach the general practice was to use predefined dictionaries (such as Fourier or wavelet transforms). However, in certain cases a dictionary that is trained to fit the input data can significantly improve the sparsity, which has applications in data decomposition, compression and analysis and has been used in the fields of image denoising and classification, video and audio processing. Sparsity and overcomplete dictionaries have immense applications in image compression, image fusion and inpainting.

MOD \cite{engan1999method} is a DL algorithm that is commonly used for extensions of Least-Squares (LS) type schemes, also known as iterative least squares dictionary learning algorithm (ILS-DLA) \cite{engan2007family}. MOD defines that if we know $\boldsymbol{S}$ in equation \ref{eq:4_eq01}, $\boldsymbol{A}$ can be estimated solving a linear LS problem. Additionally, knowing $\boldsymbol{A}$ we obtain $\boldsymbol{S}$ by solving a sparse recovery problem. MOD iterates between the two steps, starting with an initial guess of $\boldsymbol{A}$, denoted as $\hat{\boldsymbol{A}}$, which can be estimated, generated by previous dictionary learning or generated analytically. Despite - simplicity, the MOD algorithm has been criticized for its slow convergence, which is due to the fact that $\boldsymbol{A}$ and $\boldsymbol{S}$ are updated separately, which may lead to a slow convergence \cite{aharon2006rm}.

@@

Tensor data are typically highly structured, a perfect match for compressive sampling, so that the CS framework relaxes data acquisition requirements, enables compact storage, and facilitates data completion (i.e., inpainting of missing samples due to a faulty sensor or unreliable measurement) \cite{cichocki2015tensor}. Roemer \emph{et al.} \cite{roemer2014tensor} have proposed a tensor-based multidimensional extensions for MOD and K-SVD algorithms, which are respectively T-MOD and K-HOSVD, and show their improved performances numerically, for the dictionary reconstruction problem.

Considering that tensor-based algorithms can perform better for dictionary recovery problems when the dictionary size increases, according to subsection \ref{sec:4_motivation_results}, we believe that tensor-based DL algorithms can improve the discriminative sensing for classification classification problems. Therefore, we propose use tensor-based DL for learning fraudulent and legitimate data separately, and apply the learned dictionaries to reconstruct a test signal and classify it as fraud or legitimate, according to the minimum reconstruction error measured by some metrics

@@

We adopt a synthetic financial datasets for fraud detection\footnote{https://www.kaggle.com/ntnu-testimon/paysim1} in order to validate our proposal. This dataset is synthetically generated by  PaySim \cite{lopez2016paysim}, which is a financial simulator that simulates mobile money transactions based on an original dataset and provides a synthetic dataset as an approach to such a problem. PaySim uses aggregated data from the private dataset to generate a synthetic dataset that resembles the normal operation of transactions and injects malicious behavior to later evaluate the performance of fraud detection methods. PaySim simulates mobile money transactions based on a sample of real transactions extracted from one month of financial logs from a mobile money service implemented in an African country. The original logs were provided by a multinational company

The selected dataset is composed by 9 features (variables) and 2.770.408 transactions (observations). It is also provided one label that classifies each transaction as fraudulent or not. As the majority dataset of anomaly or fraud detection, the dataset of mobile money transactions is imbalanced, where the number of fraudulent transactions is 8.213 against 2.762.196 of normal transactions. Therefore, the fraud class represents 0,30 \% of the total transactions.

For evaluation of the proposed classification approach we adopt a data splitting into training and test data, where the training data has 70 \% of the whole dataset. We denote the training data as $X_r$ and the test data as $X_e$. The dataset can also be divided by normal and fraudulent transactions, where the normal train data is denoted as $X_r^o$ and the fraud train data is denoted as $X_r^f$. The same notation of fraud, normal, train and test is applied to qualify $A$ and $S$.

@@

\section{Tensor-based Sparse Representation Classification}
\label{sec:4_proposal}

We propose a Tensor-based Sparse Representation Classification approach to use tensor-based DL for learning fraudulent and legitimate dictionaries separately, and apply the learned dictionaries to reconstruct a test signal and classify it as fraud or legitimate, according to the minimum reconstruction error measured by some metrics.

Our proposal requires supervision, where labels of training data are used to classify each transaction as fraud or normal. The first step is to split the training dataset into fraud and normal classes, and create the data matrices $\boldsymbol{X}_r^f$ and $\boldsymbol{X}_r^o$, respectively. For each data matrix, we randomly select $N$ columns into a matrix and compute its data normalization in order to estimate the initial dictionaries $\boldsymbol{\hat{A}}_r^f$ and $\boldsymbol{\hat{A}}_r^o$. Afterward, we apply the dictionaries and the data matrices to the selected DL algorithms for learning the best dictionaries $\boldsymbol{A}_r^f$ and $\boldsymbol{A}_r^o$ that respectively represents fraud and normal classes as basis vectors.

With the trained dictionaries $\boldsymbol{A}_r^f$ and $\boldsymbol{A}_r^o$ and the test data $\boldsymbol{X}_e$ it is possible to process each transaction of $\boldsymbol{X}_e$, denoted as $\boldsymbol{x}_t$, where $t$ represents the transaction index, in order to compute its sparse coding from fraud and normal dictionaries, generating respectively $\boldsymbol{S}_e^f$ and $\boldsymbol{S}_e^o$. Subsequently, we compute the signal reconstruction for each test transaction $t$, as $\boldsymbol{x}_e^f = \boldsymbol{A}_r^f \cdot \boldsymbol{S}_e^f$ and $\boldsymbol{x}_e^o = \boldsymbol{A}_r^o \cdot \boldsymbol{S}_e^o$.

Finally, we compare $\boldsymbol{x}_t^f$ and $\boldsymbol{x}_t^o$ to $\boldsymbol{x}_t$ in order to evaluate the reconstruction error and to classify the transaction as fraud or normal according to the minimum reconstruction error from $\boldsymbol{x}_t^f$ and $\boldsymbol{x}_t^o$, respectively. We adopt the cosine similarity to compare the reconstructed signal to the original one.

@@

For data analysis of imbalanced classes it is usually applied a data undersample method, where an under sized sample is selected from the original dataset, with similar amount of occurrences for each class of the dataset. This method is efficient for classification algorithm training, but it faces generalization problems when tries to classify new data.

Considering that fraud or other kind of malicious events are rare when compared to legitimate events, we propose to evaluate our proposal for undersampled data and for the complete dataset, evaluating the results for training using undersample data ans testing with undersample test, as well as using the undersample data for training and the complete testing data to evaluate the classification accuracy.

The approach described in Section \ref{sec:4_proposal} can adopt any DL algorithm, however we propose to evaluate the K-HOSVD in order to analyze how a tensor-based DL algorithm can highlight the discriminative structure and relationships of one dataset. We propose to compare the proposed approach against the Support Vector Machines (SVM) algorithm and against the Logistic Regression (LR) algorithm, using features extracted trough Principal Component Analysis (PCA).

SVM is one classifier algorithm that has been successfully applied to areas ranging from handwriting recognition to text classification. SVM has also received considerable attention for classifying high-dimensional non-Gaussian data, with applications for anomaly detection. SVMs yield good generalization performance on such problems by directly estimating a decision boundary with maximal separability \cite{akbani2004applying, banerjee2006support}. LR is the most common method used to model binary response data \cite{hilbe2011logistic}, it is useful for situations in where it is necessary to predict the presence or absence of a characteristic, with binary classification, such as in anomaly or fraud detection \cite{bhattacharyya2011data}.

We adopt the area under the Receiver Operating Characteristic (ROC) curve and the area under the Precision-Recall (PR) curve in order to evaluate our approach for fraud detection from a mobile money transaction dataset, and to compare the results against the logistic regression algorithm applied to the same problem. The ROC curve makes use of the proportion of two metrics: true positives rate (TPR) and false positives rate (FPR), which are defined as:

@@

ROC curves are commonly used to present results for binary decision problems in machine learning. However, when dealing with highly skewed datasets, PR curves give a more informative picture of an algorithm’s performance \cite{davis2006relationship, he2009learning}. The PR curve is defined by plotting Precision Rate (Pr) over the Recall Rate (Rr), which are defined as:

\begin{equation}\label{eq:4_eq06}
	Pr = \frac{TP}{TP + FP},
\end{equation}

\begin{equation}\label{eq:4_eq07}
	Rr = \frac{TP}{TP + FN}.
\end{equation}

PR curves exhibit a strong correspondence to ROC curves, where a curve dominates in ROC space if and only if it dominates in PR space. However, an algorithm that optimizes the Area Under the Curve (AUC) in the ROC space is not guaranteed to optimize the AUC in PR space. Considering that our data is very imbalanced, with many more negatives than positives (frauds) values, we adopt the area under the PR curve for classification evaluation, but we also compute the area under the ROC curve as a secondary classification metric.

Additionally, we perform a cross-validation analysis in order to optimize the parameters $K$ and $N$, evaluating the values of 2, 3 and 5 for $K$ and 10, 20, 40 and 100 for $N$.

@@

Table \ref{tab:4_tab1} presents the results for fraud detection from mobile money transactions through SVM, LR with PCA and the proposed K-HOSVD-based classification.

\begin{table}[h!]
  \centering
  % \footnotesize
  \caption{Results for fraud detection from mobile money transactions} 
  \label{tab:4_tab1}
  \begin{tabular}{ c c c c c }
	\toprule
	\multirow{2}{*}{\textbf{Classifier}}   &\multicolumn{2}{c}{\textbf{undersample/undersample}} &\multicolumn{2}{c}{\textbf{undersample/complete}}\\ 
			\hhline{~----}
			&\textbf{ROC-AUC} &\textbf{PR-AUC} &\textbf{ROC-AUC} &\textbf{PR-AUC}\\
	\midrule
	SVM &0.5039 &0.7493 &0.8496 &0.8497 \\
	LR with PCA &0.9767 &0.9793 &0.5633 &0.0051 \\
	K-HOSVD ($K=3$, $N=40$) &0.8622 &0.8917 &0.8652 &0.4578 \\
    \bottomrule
  \end{tabular}
\end{table}

According to the results, the SVM algorithm presents the best PR-AUC for the scenario that evaluates the generalization performance for fraud detection of imbalanced data. However, the PR-AUC of the SVM algorithm was the worst case for training and testing with undersample data. The LR algorithm applied to PCA data presents the best results for training and testing with undersample data, although its results for the evaluation of the complete testing data presents a very low PR-AUC.

The proposed Tensor-based Sparse Representation Classification, using K-HOSVD presents higher PR-AUC than SVM for training and testing with undersample data, but its results are worst than LR with PCA for the same scenario. For training the undersample data and test with complete data, the proposed approach presents better PR-AUC than LR with PCA and the best ROC-AUC. Therefore, it is possible to observe that our approach presents average results if compared to two well known and highly adopted classifier algorithms.

% \section{Discussion}
% \undersample{sec:4_Discussion}

@@

The results shows how imbalanced data and its instance for fraud detection in mobile money transactions are challenging for classification algorithms, regarding the classification performance for undersampled data and for generalization from undersample data training to complete data testing.

It is also possible to observe that the proposed tensor-based sparse representation classification, using K-HOSVD, presents average performance and highlights some enhancement possibilities, such as:

\begin{enumerate}
	\item Extend the proposed approach to adopt one dictionary with basis vectors that represent legitimate and fraudulent data, as a concatenation or as a kronecker product, with the classification according to a sparse code comparison;
	\item Extend the proposed approach to adopt discriminative discriminative functions for T-MOD and K-HOSVD;
	\item Extend the evaluation for other DL algorithms.
\end{enumerate}
